Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-11 article/article.tex
methods

\usepackage{mathptmx}
\usepackage{graphicx,xcolor,booktabs, tabularx, amsmath}
\usepackage{times}
\newcommand{\todo}[1]{\textbf{\textcolor{blue}{Todo: #1 }}}
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

@@

\begin{equation}
\label{eq:maxLikelihood}
\operatorname{arg\,max}_i \sum_{t=1}^{N}{\log{P(C_{i}|X)}}
\end{equation}

@@

\textbf{\emph{Linear Support Vector Machine (LSVM).}} The LSVM is a discriminant based approach to classification. For an elaborate description see \cite{bk:2004aplay}. For each selected scan belonging to a stimulus, the LSVM classifies it as either a picture or a sentence. The final classification of the stimulus is

\textbf{\emph{Multivariate Gaussian (MVG).}} In MVG, independence between feature vectors is not assumed. Instead, the mutivariate distribution is used to estimate the probability of the classes, with the covariance matrix and the means as parameters. Again, the increase in parameters to be estimated compared to GNB (the correlations) may decrease generality, while also decreasing inductive bias.

- same for each algorithm:
    - What features did we select?
    - How did we train?
    - How did we test?
        - How did we calculate performance?
- algorithms:
    - gaussian naive-bayes (gnb)
        - pca + gnb
    - multivariate
    - svm
    - why multivariate is not a priori better than naive: less assumption, higher generalizability, better estimation parameters.

>>>>

\usepackage{mathptmx}
\usepackage{graphicx,xcolor,booktabs, tabularx, amsmath}
\usepackage{times}
\usepackage{breqn}
\newcommand{\todo}[1]{\textbf{\textcolor{blue}{Todo: #1 }}}
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

@@

\begin{equation}
\label{eq:maxLikelihood}
\operatorname{arg\,max}_i \sum_{t=1}^{N}{\log{P(C_{i}|x^{t})}}
\end{equation}

@@

\textbf{\emph{Linear Support Vector Machine (LSVM).}} The LSVM is a discriminant based approach to classification. For an elaborate description see \cite{bk:2004aplay}. For each selected scan belonging to a stimulus, the LSVM classifies it as either a picture or a sentence. The final classification of the stimulus is:

\begin{equation}
\label{eq:argmaxsvm}
\operatorname{arg\,max}_i \sum_{t=1}^{N}{b_{i}^{t}}
\end{equation}

where $t$ denotes the scan index and $b$ is given by:

\begin{equation}
b_{i} = \left\{
\begin{array}{l l}
1 \quad \text{if $C_{i}$ is classified}\\
0 \quad \text{otherwise}\\
\end{array} \right.
\end{equation}

\textbf{\emph{Multivariate Gaussian (MVG).}} In MVG, independence between feature vectors is not assumed. Instead, the multivariate distribution is used to estimate the probability of the classes, with the covariance matrix and the means as parameters. Again, the increase in parameters to be estimated compared to GNB (the correlations) may decrease generality, while also decreasing inductive bias.

\begin{dmath}
\label{eq:multivariate}
g_{i}(\mathbf{x}) = -\frac{d}{2}\log{2\pi}-\frac{1}{2}\log{|\Sigma_{i}|}-\frac{1}{2}(\mathbf{x}-\mu_{i})^{T}\Sigma_{i}^{-1}(\textbf{x}-\mu_{i})+\log{P(C_{i})}
\end{dmath}
